---
title: "Cancer Variant Explorer (CVE) tutorial"
author: | 
  | Andreas Mock
  | Cancer Research UK Cambridge Institute, University of Cambridge
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[ascii]{inputenc}
---

###1) Introduction

The goal of the tutorial is to present the functionality of the CVE package. CVE can be installed via Bioconductor 

```{r,eval=FALSE}
source("http://www.bioconductor.org/biocLite.R")
biocLite("CVE")
```

and once installed loaded into the R session by

```{r,eval=FALSE}
library(CVE)
```

###2) Oncotator Annotation

CVE leverages output files of the Oncotator Annotation Tool[^1] to prioritise variants. The CVE package includes the example Oncotator output file `oncotator_example` for the 1087 mutations prioritised in the melanoma case study. CVE can either work with a data frame containing the output file of one sample or a list containing multiple files.

```{r, echo=F,results="hide", eval=F}
devtools::load_all()
```


###3) Reading data and opening the shiny app

The function `openCVE` opens the CVE shiny app. It requires the oncotator output file as a data frame (output of 1 sample) or a list (output of multiple samples) and the corresponding sample name(s).  

```{r, eval=FALSE}
openCVE(oncotator_example, sample_names="case study")
```

To showcase the modularity of CVE, we added an extension for WGCNA

```{r, eval=FALSE}
openCVE(oncotator_example, sample_names="case study", extension="WGCNAmelanoma")
```

###4) Priorising variants with CVE

For details regarding prioritising variants, please refer to the paper [^2].

### Session information

```{r}
sessionInfo()
```

### References
[^1]: Ramos, A.H., Lichtenstein, L., Gupta, M., Lawrence, M.S., Pugh, T.J., Saksena, G., Meyerson, M., Getz, G.: Oncotator: Cancer Variant Annotation Tool. Human Mutation 36(4), 2423–2429 (2015)
[^2]: Mock, A., Murph, S., Morris, J., Marass, F., Rosenfeld, N., Massie, C.: CVE: an R package for interactive variant prioritisation in precision cancer medicine. 
